Manuscript Template for a Data Analysis Project

### 2023-02-03 products/manuscript/Manuscript.qmd
project part 1

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
```

@@

## Description of data and data source
The source of

## Questions/Hypotheses to be addressed
Question: Can HIV death rates be predicted by social determinants of health like poverty and/ or by HIV related outcomes (new diagnoses, prevalence PrEP use, etc?)

H0 : There is no correlation between HIV-related deaths and SDOH or HIV-related outcomes.
Ha : There is a correlation between HIV-related deaths and SDOH or HIV-related outcomes.

@@

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._
Loading the datasets from OASIS for deaths and population (Hispanic, NH White, NH Black) for persons ages 13-59 from 2018 to 2020.
```{r warning=FALSE}
setwd("../../")
his_deaths <- read_xlsx("data/raw_data/hivdeaths_his_1820.xlsx", skip = 1)
nhw_deaths <- read_xlsx("data/raw_data/hivdeaths_nhw_1820.xlsx", skip = 1)
nhb_deaths <- read_xlsx("data/raw_data/hivdeaths_nhb_1820.xlsx", skip = 1)

his_pop <- read_xlsx("data/raw_data/pop_his_1820.xlsx", skip = 1)
nhw_pop <- read_xlsx("data/raw_data/pop_nhw_1820.xlsx", skip = 1)
nhb_pop <- read_xlsx("data/raw_data/pop_nhb_1820.xlsx", skip = 1)
```

Loading dataset from AIDSVu for social determinants of health (2020) and new HIV diagnoses from 2018 to 2020.
```{r warning=FALSE}
setwd("../../")
sdoh <- read_xlsx("data/raw_data/AIDSVu_County_SDOH_2020.xlsx", skip = 3)
sdoh <- sdoh %>%  filter(State == "Georgia")

dx18 <- read_xlsx("data/raw_data/AIDSVu_County_NewDX_2018.xlsx", skip = 3)
dx18 <- dx18 %>%  filter(State == "Georgia") %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

dx19 <- read_xlsx("data/raw_data/AIDSVu_County_NewDX_2019.xlsx", skip = 3)
dx19 <- dx19 %>%  filter(State == "Georgia")%>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

dx20 <- read_xlsx("data/raw_data/AIDSVu_County_NewDX_2020.xlsx", skip = 3)
dx20 <- dx20 %>%  filter(State == "Georgia") %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))
```

Let's load data from Georgia Data on Poverty rates in Georgia by race/ ethnicity for the period 2016-2020.
```{r warning = false}
setwd("../../")
pov <- read_xlsx("data/raw_data/economics_22.xlsx", sheet = "poverty")

glimpse(pov)
```

We'll just be using the data from the "2016-2020 Persons Below Poverty Level" by race/ethnicity. We'll also change the text formatting of County to match the other data frames.
```{r}
pov <- pov %>%  select(1, starts_with("2016-2020 Persons Below Poverty Level"))

pov$County <- str_to_title(pov$County)
```

Let's do some cleaning on the OASIS data. We'll remove extra columns and rows, as well as rows with "Selected ages/sexes total", pivot Year and Deaths into long format, and create the new variable for race/ethnicity.
```{r}
his_deaths <- his_deaths[c(-1,-2387:-2414),-7]
his_deaths <- his_deaths %>% filter(!grepl("Selected", Age)) %>% filter(!grepl("Selected", Sex)) %>%
  pivot_longer(c(4:6), names_to = "Year", values_to = "HIV_Deaths") %>% 
  mutate("Race_Ethnicity" = "Hispanic")

nhw_deaths <- nhw_deaths[c(-1,-2387:-2414),-7]
nhw_deaths <- nhw_deaths %>% filter(!grepl("Selected", Age)) %>% filter(!grepl("Selected", Sex)) %>%
  pivot_longer(c(4:6), names_to = "Year", values_to = "HIV_Deaths") %>% 
  mutate("Race_Ethnicity" = "NH White")

nhb_deaths <- nhb_deaths[c(-1,-2387:-2414),-7]
nhb_deaths <- nhb_deaths %>% filter(!grepl("Selected", Age)) %>% filter(!grepl("Selected", Sex)) %>%
  pivot_longer(c(4:6), names_to = "Year", values_to = "HIV_Deaths") %>% 
  mutate("Race_Ethnicity" = "NH Black")
```

Next, we'll merge the datasets into one dataframe, and remove the original datasets from the environment.
```{r}
deaths <- full_join(his_deaths, nhw_deaths)
deaths <- full_join(deaths, nhb_deaths)

rm(his_deaths, nhw_deaths, nhb_deaths)
```

Next, let's clean up the dataset for population using a similar method.
```{r}
his_pop <- his_pop[c(-1,-2387:-2412),-7]
his_pop <- his_pop %>% filter(!grepl("Selected", Age)) %>% filter(!grepl("Selected", Sex)) %>% 
  pivot_longer(c(4:6), names_to = "Year", values_to = "Population") %>% 
  mutate("Race_Ethnicity" = "Hispanic")

nhw_pop <- nhw_pop[c(-1,-2387:-2412),-7]
nhw_pop <- nhw_pop %>% filter(!grepl("Selected", Age)) %>% filter(!grepl("Selected", Sex)) %>% 
  pivot_longer(c(4:6), names_to = "Year", values_to = "Population") %>% 
  mutate("Race_Ethnicity" = "NH White")

nhb_pop <- nhb_pop[c(-1,-2387:-2412),-7]
nhb_pop <- nhb_pop %>% filter(!grepl("Selected", Age)) %>% filter(!grepl("Selected", Sex)) %>% 
  pivot_longer(c(4:6), names_to = "Year", values_to = "Population") %>% 
  mutate("Race_Ethnicity" = "NH Black")
```

Merging datasets and cleaning the original from the environment.
```{r}
pop <- full_join(his_pop, nhw_pop)
pop <- full_join(pop, nhb_pop)

rm(his_pop, nhw_pop, nhb_pop)
```

Next, let's merge the two OASIS dataframes.
```{r}
df <- full_join(deaths, pop, by = c("Geography", "Sex", "Age", "Year", "Race_Ethnicity"))
```

Next, let's create a new variable for Public Health District, change some variable to factors, and rename the Age variable and Geography variable.
```{r}
df <- df %>% rename(County = Geography) %>% 
  mutate(District = case_when(County %in% c("Bartow", "Catoosa", "Chattooga", "Dade", "Floyd", "Gordon", "Haralson", "Paulding", "Polk", "Walker") ~ "1-1",
 County %in% c("Cherokee", "Fannin", "Gilmer", "Murray", "Pickens", "Whitfield") ~ "1-2",
 County %in% c("Banks", "Dawson", "Forsyth", "Franklin", "Habersham", "Hall", "Hart", "Lumpkin", "Rabun", "Stephens", "Towns", "Union", "White") ~ "2",
 County %in% c("Cobb", "Douglas") ~ "3-1",
 County %in% c("Fulton") ~ "3-2",
 County %in% c("Clayton") ~ "3-3",
 County %in% c("Gwinnett", "Newton", "Rockdale") ~ "3-4",
 County %in% c("DeKalb") ~ "3-5",
 County %in% c("Butts", "Carroll", "Coweta", "Fayette", "Heard", "Henry", "Lamar", "Meriwether", "Pike", "Spalding", "Troup", "Upson") ~ "4",
 County %in% c("Bleckley", "Dodge", "Johnson", "Laurens", "Montgomery", "Pulaski", "Telfair", "Treutlen", "Wheeler", "Wilcox") ~ "5-1",
 County %in% c("Baldwin", "Bibb", "Crawford", "Hancock", "Houston", "Jasper", "Jones", "Monroe", "Peach", "Putnam", "Twiggs", "Washington", "Wilkinson") ~ "5-2",
 County %in% c("Burke", "Columbia", "Emanuel", "Glascock", "Jefferson", "Jenkins", "Lincoln", "McDuffie", "Richmond", "Screven", "Taliaferro", "Warren", "Wilkes") ~ "6",
 County %in% c("Chattahoochee", "Clay", "Crisp", "Dooly", "Harris", "Macon", "Muscogee", "Marion", "Quitman", "Randolph", "Schley", "Stewart", "Sumter", "Talbot", "Taylor", "Webster") ~ "7",
 County %in% c("Ben Hill", "Berrien", "Brooks", "Cook", "Echols", "Irwin", "Lanier", "Lowndes", "Tift", "Turner") ~ "8-1",
 County %in% c("Baker", "Calhoun", "Colquitt", "Dougherty", "Decatur", "Early", "Grady", "Lee", "Miller", "Mitchell", "Seminole", "Terrell", "Thomas", "Worth") ~ "8-2",
 County %in% c("Bryan", "Camden", "Chatham", "Effingham", "Glynn", "Liberty", "Long", "McIntosh") ~ "9-1",
 County %in% c("Appling", "Atkinson", "Bacon", "Brantley", "Bulloch", "Candler", "Charlton", "Clinch", "Coffee", "Evans", "Jeff Davis", "Pierce", "Tattnall", "Toombs", "Ware", "Wayne") ~ "9-2",
 County %in% c("Barrow", "Clarke", "Elbert", "Greene", "Jackson", "Madison", "Morgan", "Oconee", "Oglethorpe", "Walton") ~ "10")) %>% 
   mutate(District = as.factor(District)) %>% 
   mutate(Sex = as.factor(Sex)) %>% 
   mutate(Age = as.factor(Age)) %>% 
   mutate(County = as.factor(County)) %>% 
   mutate(Race_Ethnicity = as.factor(Race_Ethnicity)) %>% 
   rename(Age_Group = Age) %>% 
   mutate(Age_Group = as.factor(Age_Group))
```

Let's clean up the Age_Group variable by removing text
```{r}
df$Age_Group <- str_replace(df$Age_Group, " Adolescence", "")
df$Age_Group <- str_replace(df$Age_Group, " Early Adulthood", "")
df$Age_Group <- str_replace(df$Age_Group, " Young Adulthood", "")
df$Age_Group <- str_replace(df$Age_Group, " Middle Adulthood", "")
```

```{r}
glimpse(df)
```
Things are looking good so far!

Now let's move onto the AIDSVu data. First, we'll merge all new HIV diagnoses from 2018-2020 into one dataframe
```{r}
dx <- full_join(dx18, dx19)
dx <- full_join(dx, dx20)
```

Let's remove columns for race/ethnicities other than Hispanic, NH White, and NH Black, as well as some other variables we won't be using in this analysis. We will also rename county and create the district variable. 
```{r}
dx <- dx %>% select(!contains(c("Asian", "American", "Multiracial", "Hawaiian", "MSM", "2013", "GEO ID", "State")))%>% 
  rename(County = "County Name")

dx$Geography <- str_remove(dx$County, " County")

dx <-  dx %>% mutate(District = case_when(County %in% c("Bartow", "Catoosa", "Chattooga", "Dade", "Floyd", "Gordon", "Haralson", "Paulding", "Polk", "Walker") ~ "1-1",
 County %in% c("Cherokee", "Fannin", "Gilmer", "Murray", "Pickens", "Whitfield") ~ "1-2",
 County %in% c("Banks", "Dawson", "Forsyth", "Franklin", "Habersham", "Hall", "Hart", "Lumpkin", "Rabun", "Stephens", "Towns", "Union", "White") ~ "2",
 County %in% c("Cobb", "Douglas") ~ "3-1",
 County %in% c("Fulton") ~ "3-2",
 County %in% c("Clayton") ~ "3-3",
 County %in% c("Gwinnett", "Newton", "Rockdale") ~ "3-4",
 County %in% c("DeKalb") ~ "3-5",
 County %in% c("Butts", "Carroll", "Coweta", "Fayette", "Heard", "Henry", "Lamar", "Meriwether", "Pike", "Spalding", "Troup", "Upson") ~ "4",
 County %in% c("Bleckley", "Dodge", "Johnson", "Laurens", "Montgomery", "Pulaski", "Telfair", "Treutlen", "Wheeler", "Wilcox") ~ "5-1",
 County %in% c("Baldwin", "Bibb", "Crawford", "Hancock", "Houston", "Jasper", "Jones", "Monroe", "Peach", "Putnam", "Twiggs", "Washington", "Wilkinson") ~ "5-2",
 County %in% c("Burke", "Columbia", "Emanuel", "Glascock", "Jefferson", "Jenkins", "Lincoln", "McDuffie", "Richmond", "Screven", "Taliaferro", "Warren", "Wilkes") ~ "6",
 County %in% c("Chattahoochee", "Clay", "Crisp", "Dooly", "Harris", "Macon", "Muscogee", "Marion", "Quitman", "Randolph", "Schley", "Stewart", "Sumter", "Talbot", "Taylor", "Webster") ~ "7",
 County %in% c("Ben Hill", "Berrien", "Brooks", "Cook", "Echols", "Irwin", "Lanier", "Lowndes", "Tift", "Turner") ~ "8-1",
 County %in% c("Baker", "Calhoun", "Colquitt", "Dougherty", "Decatur", "Early", "Grady", "Lee", "Miller", "Mitchell", "Seminole", "Terrell", "Thomas", "Worth") ~ "8-2",
 County %in% c("Bryan", "Camden", "Chatham", "Effingham", "Glynn", "Liberty", "Long", "McIntosh") ~ "9-1",
 County %in% c("Appling", "Atkinson", "Bacon", "Brantley", "Bulloch", "Candler", "Charlton", "Clinch", "Coffee", "Evans", "Jeff Davis", "Pierce", "Tattnall", "Toombs", "Ware", "Wayne") ~ "9-2",
 County %in% c("Barrow", "Clarke", "Elbert", "Greene", "Jackson", "Madison", "Morgan", "Oconee", "Oglethorpe", "Walton") ~ "10")) %>% 
  mutate(District = as.factor(District))
```

Things are looking pretty good so frame, so let's save these dataframes.
```{r}
saveRDS(df, "../../data/df.rds")
saveRDS(dx, "../../data/dx.rds")
saveRDS(sdoh, "../../data/sdoh.rds")
saveRDS(pov, "../../data/pov.rds")
```

Clear the environment and start fresh.
```{r}

```
## Statistical analysis
Explore central tendency across demographic groups. Fit a poisson regression model predicting death-to-case ratio from percentage with x SDOH variables and percentage of x demographic group.

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(readxl)
library(lubridate)
```

@@

## Description of data and data source
The data used in this analysis was retrieved from AIDSVu, a publicly available data source presented by Emory University's Rollins School of Public Health and partners, whose mission is to make HIV data widely available and accessible. AIDSVu compiled the data used in this analysis from the CDC. These datasets contain data collected at the state-level from 2020 on: new HIV diagnoses, HIV-related deaths, counts/ percentages of those with late HIV diagnoses, viral suppression, PrEP coverage, HIV prevalence, and state testing, and social determinants of health. These datasets contain demographic-level information for sex, race/ethnicity, transmission category, among others.

## Questions/Hypotheses to be addressed
Question: Can HIV mortality-prevalence ratio at the state-level in the United States be predicted by social determinant of health (ex. poverty rates), percentage of people living with HIV (PLWH) who are virally suppressed, and/ or percentage of late diagnoses/ percentage of minority HIV deaths?

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7842853/

where mortality-prevalence ratio = (number of deaths/number of prevalant cases) / prevelance rate

H0 : Death-to-case ratio is not correlated with differences in demographic factors, social determinants of health, testing prevalence, or factors influencing HIV outcomes, such as late diagnoses, viral suppression, and PrEP coverage.

HA : Death-to-case ratio is  correlated with differences in demographic factors, social determinants of health, testing prevalence, or factors influencing HIV outcomes, such as late diagnoses, viral suppression, and PrEP coverage.

Special interest will be given to those disproportionately impacted by HIV, including Non-Hispanic Black populations and the MSM community.

@@

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._
Loading the datasets.
```{r}
deaths <- read_xlsx("../../data/raw_data/AIDSVu_State_Death_2020.xlsx", skip = 3)
dx <- read_xlsx("../../data/raw_data/AIDSVu_State_NewDX_2020.xlsx", skip = 3)
```

##Selecting only states/ districts in the South geographic region, as defined by the CDC.
```{r}
deaths <- deaths %>% filter(State %in% c("Alabama", "Arkansas", "Delaware", "Washington, D.C.", "Florida", "Georgia", "Kentucky", "Louisiana", "Maryland", "Mississippi", "North Carolina", "Oklahoma", "South Carolina", "Tennessee", "Texas", "Virginia", "West Virginia")) %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

sex_deaths_sub <- deaths %>% select(1:7)
race_deaths_sub <- deaths  %>% select(c(1:5, 8:14))
age_deaths_sub <- deaths  %>% select(c(1:5, 15:19))

sex_deaths_sub <- sex_deaths_sub %>% pivot_longer(6:7, names_to = "Sex", values_to = "Death Rate by Sex")
sex_deaths_sub$Sex <- gsub(" Death Rate", "", sex_deaths_sub$Sex)
sex_deaths_sub <- sex_deaths_sub %>% mutate_if(is.character, as.factor) %>% 
  mutate(`GEO ID` = as.factor(`GEO ID`))

race_deaths_sub <- race_deaths_sub  %>% pivot_longer(6:12, names_to = "Race/Ethnicity", values_to = "Death Rate by Race/Ethnicity")
race_deaths_sub$`Race/Ethnicity` <- gsub(" Death Rate", "",race_deaths_sub$`Race/Ethnicity`)
race_deaths_sub <- race_deaths_sub %>% mutate_if(is.character, as.factor) %>% 
  mutate(`GEO ID` = as.factor(`GEO ID`))

age_deaths_sub <- age_deaths_sub %>% pivot_longer(6:10, names_to = "Age_Group", values_to = "Death Rate by Age Group")
age_deaths_sub$Age_Group <- gsub("Age ", "", age_deaths_sub$Age_Group)
age_deaths_sub$Age_Group <- gsub(" Death Rate", "", age_deaths_sub$Age_Group)

age_deaths_sub <- age_deaths_sub %>% mutate_if(is.character, as.factor) %>% 
  mutate(`GEO ID` = as.factor(`GEO ID`))
```

```{r}
dx <- dx %>% filter(State %in% c("Alabama", "Arkansas", "Delaware", "Washington, D.C.", "Florida", "Georgia", "Kentucky", "Louisiana", "Maryland", "Mississippi", "North Carolina", "Oklahoma", "South Carolina", "Tennessee", "Texas", "Virginia", "West Virginia")) %>% 
  select(!contains(c("Rate Stability", "Percent", "Case")))

sex_dx_sub <- dx %>% select(1:7)
race_dx_sub <- dx %>% select(c(1:5, 8:14))
age_dx_sub <- dx %>% select(c(1:5, 15:19))

sex_dx_sub <- sex_dx_sub %>% pivot_longer(6:7, names_to = "Sex", values_to = "New Diagnoses Rate by Sex")
sex_dx_sub$Sex <- gsub("New Diagnoses ", "", sex_dx_sub$Sex)
sex_dx_sub$Sex <- gsub(" Rate", "", sex_dx_sub$Sex)
sex_dx_sub <- sex_dx_sub %>% mutate_if(is.character, as.factor) %>% 
  mutate(`GEO ID` = as.factor(`GEO ID`))

race_dx_sub <- race_dx_sub  %>% pivot_longer(6:12, names_to = "Race/Ethnicity", values_to = "New Diagnoses Rate by Race/Ethnicity")
race_dx_sub$`Race/Ethnicity` <- gsub("New Diagnoses ", "", race_dx_sub$`Race/Ethnicity`)
race_dx_sub$`Race/Ethnicity` <- gsub(" Rate", "", race_dx_sub$`Race/Ethnicity`)
race_dx_sub <- race_dx_sub %>% mutate_if(is.character, as.factor) %>% 
  mutate(`GEO ID` = as.factor(`GEO ID`))

age_dx_sub <- age_dx_sub %>% pivot_longer(6:10, names_to = "Age_Group", values_to = "New Diagnoses Rate by Age Group")
age_dx_sub$Age_Group <- gsub("New Diagnoses Age ", "", age_dx_sub$Age_Group)
age_dx_sub$Age_Group <- gsub(" Rate", "", age_dx_sub$Age_Group)
age_dx_sub <- age_dx_sub %>% mutate_if(is.character, as.factor) %>% 
  mutate(`GEO ID` = as.factor(`GEO ID`))
```

Calculate mortality to incidence ratio (MIR) "The mortality-to-incidence ratio (MIR) can be computed from readily accessible, public-use data on cancer incidence and mortality, and a high MIR value is an indicator of poor survival relative to incidence."

The IMR (incidence:mortality ratio) is defined as the ratio of the number of people who become HIV infected per year to the number of people among those already infected who die (from any cause) per year. When this number is greater than one, the size of the population of PLHIV grows; when it is less than one, the size of that population shrinks 
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6201869/#!po=16.6667

https://www.kff.org/global-health-policy/issue-brief/assessing-global-hiv-targets-in-pepfar-countries-a-dashboard/
```{r}
sex_df <- full_join(sex_deaths_sub, sex_dx_sub)

sex_df  <- sex_df %>% group_by(State, Sex) %>%
  mutate(d2c_ratio_sex = sum(`Death Rate by Sex`/`New Diagnoses Rate by Sex`)) %>% 
  mutate(d2c_ratio_sex = round(d2c_ratio_sex, 1))

race_df <- full_join(race_deaths_sub, race_dx_sub)

race_df <- race_df %>% group_by(State, `Race/Ethnicity`) %>%
  mutate(d2c_ratio_race = sum(`Death Rate by Race/Ethnicity`/`New Diagnoses Rate by Race/Ethnicity`)) %>% 
  mutate(d2c_ratio_race = round(d2c_ratio_race, 1))

age_df <- full_join(age_deaths_sub, age_dx_sub)

age_df <- age_df %>% group_by(State, Age_Group) %>%
  mutate(d2c_ratio_age = sum(`Death Rate by Age Group`/`New Diagnoses Rate by Age Group`)) %>% 
  mutate(d2c_ratio_age = round(d2c_ratio_age, 1))

saveRDS(sex_df, "../../data/sex_df.rds")
saveRDS(race_df, "../../data/race_df.rds")
saveRDS(age_df, "../../data/age_df.rds")
```

```{r}
rm(list=ls())

sex_df <- readRDS("../../data/sex_df.rds")
race_df <- readRDS("../../data/race_df.rds")
age_df <- readRDS("../../data/age_df.rds")

```

```{r}

```

```{r}
df <- full_join(deaths, new_dx)
df <- full_join(df, prep)
df<- full_join(df, prev)

df <- df %>% select(!contains("Rate Stability"))

saveRDS(df, "../../data/raw_data/raw_df.rds")

rm(list=ls())
rm(list=ls())

prep <- read_xlsx("../../data/raw_data/AIDSVu_State_PrEP_2020.xlsx", skip = 3)
prep <- prep %>% select(!contains("Rate Stability"))

df <- readRDS("../../data/raw_data/raw_df.rds")

late_dx <- read_xlsx("../../data/raw_data/AIDSVu_State_LateDiagnoses_2020.xlsx", skip = 3)
sdoh <- read_xlsx("../../data/raw_data/AIDSVu_State_SDOH_2020.xlsx", skip = 3)
v_sup <- read_xlsx("../../data/raw_data/AIDSVu_State_ViralSuppression_2020.xlsx", skip = 3)
testing  <- read_xlsx("../../data/raw_data/AIDSVu_State_Testing_2020.xlsx", skip = 3)
```
## Statistical analysis
Explore central tendency across demographic groups. Fit a poisson regression model predicting death-to-case ratio from percentage with x SDOH variables and percentage of x demographic group.
